---
title: "IPLMatchest-test - project 3"
author: "SKoka"
date: "6/24/2019"
output: html_document
---

Introduction: 

  IPL - The Indian Premier League (IPL) is a professional Twenty20 cricket league in India contested
  during March or April and May of every year by eight teams representing eight different cities in India.
  In project 1, we implemented data cleaning process of the IPL data set which picked up from the kaggle website
  In project2, we will implementing the statistical inference of the IPL dataset byy using the 
  ggplot - geom_bar(), geom_dotplot() and geom_point().
  Performed t-test where the p values is very less, reject the null hypothesis
  Below we will be covering,
  1. Number of times each team won the toss
  2. Number of games played in each city
  3. Number of games won by each team
  4. Percentage of each teams winning
  5. Each teams won by runs for all the games


```{r}
matches <- read.csv("matches.csv")
```


```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

```
# GGPlots
## 1. Number of times each team won the toss
### Prepare the data - filter na toss win games
```{r}
nonNullTWMatches <- matches[which(!is.na(matches$toss_winner)),]

```

```{r}

ggplot(nonNullTWMatches,aes(toss_winner,fill= toss_winner)) +geom_bar() + theme(axis.text.x = element_text(angle = 90))+ ylab("# of Games")

```
## Number of games played in each city
### Prepare the data - filter na city games
```{r}
nonNullCityMatches <- matches[which(!is.na(matches$city)),]
```

```{r}
ggplot(nonNullCityMatches,aes(city,fill= city)) +geom_dotplot() + theme(axis.text.x = element_text(angle = 90))+ ylab("# of Games")

```

## Count of win games
### Prepare the data - filter na and tie result games
```{r}
wonMatches <- matches[matches$result=="normal",]

```

```{r}
ggplot(wonMatches,aes(winner,fill= winner)) +geom_bar() + theme(axis.text.x = element_text(angle = 90))+ ylab("# of Games")


```
## ggplot of winning percentage
### Prepare the data - collect the number matches as team 1

```{r}
asT1<- table(matches$team1)
```
### Prepare the data - collect the number matches as team 2
```{r}
asT2<- table(matches$team2)
```
# Summ of team1 and team2

```{r}
consolidatedT <- asT1 + asT2
```

### Prepare the data - collect the number matches won by each team
```{r}
wonCount <- table(wonMatches$winner)
```

## Convert into Data frame
```{r}
matches$winner[matches$winner==""] <- NA
resultG <- matches[which(!is.na(matches$winner)),]
wgames <- matches[matches$result=="normal",]
w <- table(wgames$winner)
gamesW <- data.frame(w)
gamesW$Var1[gamesW$Var1 == ""] <-NA
resultCountFinal <- gamesW[which(!is.na(gamesW$Var1)),]
resultCountFinal
resultDF <- data.frame(resultCountFinal)
colnames(resultDF)[1]<-"Team Name"
colnames(resultDF)[2]<-"NumberOfGamesWon"
resultDF


```
```{r}
gamesDF <- data.frame(consolidatedT)
colnames(gamesDF)[1]<-"Team Name"
colnames(gamesDF)[2]<-"NumberOfGames"
gamesDF
```
### ggplot of number of games won percentage over number of games played

```{r}
ggplot(left_join(gamesDF,resultDF ),aes(resultDF$`Team Name`,resultDF$NumberOfGamesWon*100/gamesDF$NumberOfGames,fill = resultDF$`Team Name`)) + geom_bar(stat = "identity") + theme(axis.text.x = element_text(angle = 90))+ xlab("Team")+ ylab("Games Won %")
```
```{r}
wonByRUns <- matches[matches$win_by_runs!=0,]
wonByRUns
```

##ggplot by using geom_point, which shows each team won by runs for all the games played

```{r}
ggplot(matches[matches$win_by_runs!=0,],aes(id,win_by_runs,col= winner )) + geom_point() +
  ylab("Won by runs ") + xlab("Runs")
  
```


```{r}
boxplot(matches$win_by_runs,matches$winner)
```
## independent 2-group t-test, where both are numeric parameters
```{r}
res <- t.test(matches$win_by_runs,matches$win_by_wickets)
res
```

## independent 2-group t-test, where both are numeric parameters, with alternative two sided, in both the tests, the P-Value is very small, we reject the null hypothesis
```{r}
t.test(matches$win_by_runs,matches$win_by_wickets,paired = TRUE, alternative = "two.sided")

```
